# This file describes how the datasets used in this Shiny were generated
# Most of this code is adapted from "RNA expression levels in human breast cancer cell line panel.Rmd", 
# by Esmee Koedoot, written on 22 November 2016 and "HL200730 RNA expression for multiple genes.Rmd",
# by Hanneke Leegwater
# Hanneke Leegwater. 10-09-2020 and 21-01-2021


# R libraries & preparation
```{r}
library(tidyverse)
library(vroom)
```

# Files to analyze
```{r}
input_file <- "original_files/20161223_ProteomicsDF.txt"
metadata_file <- "original_files/breast_cancer_subtypes.csv"
```

# Read cell line proteomics data
And remove cell line MDAMB435s. 
Also, remove some MDAMB468 types to reduce bias towards shared MDA-MB-468 properties
and remove some SUM159 types to reduce bias towards SUM159PT properties and remove
OCUBM, HBC100 and UACC812 because their subtype is not well documented
## Add missing cell lines from Dai et al 2017 paper. 
```{r}
## Read file
cell_line_dataprot <- vroom::vroom(input_file, col_types = cols()) %>%
  select(-NAME, -MDAMB435s) %>%
  select(-MDAMB468GFP, -MDAMB468LV105, -MDAMB468LV122, -MDAMB468PT) %>%
  select(-SUM1597B3, -SUM1597C6, -OCUBM, -HBC100, -UACC812) %>%
  rename("Hs578T" = "HS578T", "SUM1315MO2" = "SUM1315M02") %>%
  column_to_rownames("UNIQID")

cell_line_dataprot <- rownames_to_column(cell_line_dataprot, "ENSEMBL_ID")
dim(cell_line_dataprot)
head(cell_line_dataprot)
```

# 3D cell line metadata
```{r}
cell_line_metadataprot <- vroom::vroom(metadata_file, col_types = cols()) %>%
  filter(CellLine %in% colnames(cell_line_dataprot))
  

dim(cell_line_metadataprot)
head(cell_line_metadataprot)
```


# Write to file
```{r}
save(cell_line_dataprot, cell_line_metadataprot, file = "cell_line_dataprot_for_shiny.RData")
```