# This file describes how the datasets used in this Shiny were generated
# Most of this code is adapted from "RNA expression levels in human breast cancer cell line panel.Rmd", 
# by Esmee Koedoot, written on 22 November 2016 and "HL200730 RNA expression for multiple genes.Rmd",
# by Hanneke Leegwater
# Hanneke Leegwater. 10-09-2020 and 21-01-2021


# R libraries & preparation
```{r}
library(tidyverse)
library(vroom)
```

# Files to analyze
```{r}
input_file <- "original_files/20161208_NormalizedCountTable_AllBCCellLineSamples.txt"
metadata_file <- "original_files/breast_cancer_subtypes.csv"
```

# Read cell line data and log2 transform
 
```{r}
## Read file
cell_line_data3D <- vroom::vroom(input_file, col_types = cols()) %>%
  select('ensembl',contains("3D_A"))%>%
  column_to_rownames("ensembl")
colnames(cell_line_data3D) <- gsub("_3D_A","", colnames(cell_line_data3D))

## Rename mislabeled cell line
cell_line_data3D <- rename(cell_line_data3D, "MDAMB175VII" = "MDAMB175")
## Log 2 transform
cell_line_data3D <- log2(cell_line_data3D + 1) %>%
  round(digits = 2)

cell_line_data3D <- rownames_to_column(cell_line_data3D, "ENSEMBL_ID")
dim(cell_line_data3D)
head(cell_line_data3D)
```

# 3D cell line metadata
```{r}
cell_line_metadata3D <- vroom::vroom(metadata_file, col_types = cols()) %>%
  filter(CellLine %in% colnames(cell_line_data3D))
dim(cell_line_metadata3D)
head(cell_line_metadata3D)
```


# Write to file
```{r}
save(cell_line_data3D, cell_line_metadata3D, file = "cell_line_data3D_for_shiny.RData")
```