# This file describes how the datasets used in this Shiny were generated
# Most of this code is adapted from "RNA expression levels in human breast cancer cell line panel.Rmd", 
# by Esmee Koedoot, written on 22 November 2016 and "HL200730 RNA expression for multiple genes.Rmd",
# by Hanneke Leegwater
# Hanneke Leegwater. 29-08-2020 & 21-01-2021.


# R libraries & preparation
```{r}
library(tidyverse)
library(vroom)
```

# Files to analyze
```{r}
input_file <- "original_files/20161122_NormalizedCounts_2DCellLines.txt"
metadata_file <- "original_files/breast_cancer_subtypes.csv"
```

# Read cell line data and log2 transform
And remove cell line MBA-MD-435s 
```{r}
## Read file
cell_line_data2D <- vroom::vroom(input_file, col_types = cols()) %>%
  column_to_rownames("EnsemblID") %>%
  select(-MDAMB435s_2D_A)
colnames(cell_line_data2D) <- gsub("_2D_A","", colnames(cell_line_data2D))

## Log 2 transform
cell_line_data2D <- log2(cell_line_data2D + 1) %>%
  round(digits = 2)

cell_line_data2D <- rownames_to_column(cell_line_data2D, "ENSEMBL_ID")
dim(cell_line_data2D)
head(cell_line_data2D)
```



# 2D cell line metadata
```{r}
cell_line_metadata2D <- vroom::vroom(metadata_file, col_types = cols())
dim(cell_line_metadata2D)
head(cell_line_metadata2D)
```


# Write to file
```{r}
save(cell_line_data2D, cell_line_metadata2D, file = "cell_line_data2D_for_shiny.RData")
```

